Title Goes Here

### 2021-03-30 analysis/paper/paper.Rmd
Agrega justificación de ondas zonales
Closes #7

>>>>

We computed the amplitude and phase of the zonal wave 1 by averaging (area-weighted) variables (temperature, geopotential height, ozone mixing ratio and Total Ozone Column) between `r knitr::combine_words(LatLabel(o3wave_lats))` for each SON and extracting the wave-1 component of the Fourier spectrum. We chose this latitude band because it is wide enough to capture most of the relevant anomalies.
